---
title: "Meteorites Analysis"
output: html_notebook
---

# Bring in code to load and clean data
```{r}
source("load_clean_meteorites.R")
```


# 10 largest meteorites
```{r}
meteorite_landings %>% 
  select(name, year, mass_g) %>% 
  slice_max(mass_g, n = 10)
```


#Average mass of fell vs found meteorites
```{r}
meteorite_landings %>%
  group_by(fall) %>% 
  summarise(mean_mass = mean(mass_g))
```


# Number of meteorites per year since 2000
```{r}
meteorite_landings %>% 
  filter(year >= 2000) %>% 
  group_by(year) %>% 
  summarise(number_of_meteorites  = n()) %>% 
  arrange(year)
```

# Number of meteorites by century
```{r}
meteorite_landings_century <- 
meteorite_landings %>% 
  mutate(century = case_when(
    is.na(year) ~ "Date not available",
    year <= 0 ~ "Please check observation for error - year <= 0",
    year < 1600 ~ "1500s and earlier",
    year < 1700 ~ "1600s",
    year < 1800 ~ "1700s",
    year < 1900 ~ "1800s",
    year < 2000 ~ "1900s",
    year < 2100 ~ "2000s",
    TRUE ~ "Please check observation for error - year not recognised"
  )
  ) 
meteorite_landings_century %>%   
  group_by(century) %>% 
  summarise(number_of_meteorites  = n())
  

```

# Check if names are unique
```{r}
meteorite_landings %>% 
  group_by(name) %>% 
  summarise(number_times_name_used = n()) %>% 
  filter(number_times_name_used > 1) %>% 
  arrange(desc(number_times_name_used))
```

#  check where lat & long = 0
Checking these as my cleaning package sets NAs to 0

There are a lot in the 2000s - might be worth checking if there's an issue with the data.

```{r}
meteorite_landings_century %>% 
  filter(latitude == 0 & longitude == 0) %>% 
  group_by(century) %>% 
  summarise(count = n())
```

# Check if any meteorites share my name!

```{r}
meteorite_landings_century %>% 
  select(name, year, mass_g) %>% 
  filter(
    str_detect(name,"[nN]eil")|
    str_detect(name,"[aA]llan")
      ) %>% 
  arrange(name)
```

